---
title: "Technical Glossary"
format: 
  html:
    theme: cosmo
    toc: true
    toc-location: left
    css: styles.css
    code-fold: true
    df-print: paged
---

```{r setup, include=FALSE}
library(yaml)
library(dplyr)
library(DT)
library(knitr)

# Read the glossary data
glossary_data <- yaml::read_yaml("entries.yaml")
entries <- glossary_data$entries

# Convert to data frame and sort alphabetically
df <- do.call(rbind, lapply(entries, function(x) {
  data.frame(
    Term = x$term,
    Definition = x$definition,
    Tags = paste(x$tags, collapse = ", "),
    Links = if(!is.null(x$links)) {
      paste(sapply(x$links, function(link) {
        paste0('<a href="', link$url, '" target="_blank">', link$title, '</a>')
      }), collapse = "<br>")
    } else "",
    stringsAsFactors = FALSE
  )
})) %>%
  arrange(Term)
```

# Welcome to the Glossary

This glossary contains technical terms and definitions. Use the search box below to find specific terms, or browse by category using the tag filters.

## Browse All Terms

```{r glossary-table, echo=FALSE}
# Create the interactive table
DT::datatable(
  df,
  escape = FALSE,
  options = list(
    pageLength = 25,
    lengthMenu = c(10, 25, 50, 100),
    searchHighlight = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel'),
    columnDefs = list(
      list(width = '20%', targets = 0),  # Term column
      list(width = '45%', targets = 1),  # Definition column
      list(width = '20%', targets = 2),  # Tags column
      list(width = '15%', targets = 3)   # Links column
    )
  ),
  filter = 'top',
  colnames = c('Term', 'Definition', 'Tags', 'Related Links'),
  caption = 'Use the search boxes above each column to filter results'
)
```

## Statistics

```{r stats, echo=FALSE}
total_terms <- nrow(df)
unique_tags <- length(unique(unlist(strsplit(df$Tags, ", "))))

cat("**Total Terms:** ", total_terms, "\n\n")
cat("**Unique Tags:** ", unique_tags, "\n\n")
```

## Tag Cloud

```{r tag-cloud, echo=FALSE}
# Extract all tags and count frequency
all_tags <- unlist(strsplit(df$Tags, ", "))
tag_counts <- table(all_tags)
tag_df <- data.frame(
  Tag = names(tag_counts),
  Count = as.numeric(tag_counts)
) %>% 
  arrange(desc(Count))

kable(tag_df, caption = "Tag Frequency")
```

---

## Contributing

To add new terms to this glossary:

1. Edit the `entries.yaml` file
2. Follow the existing format:
   ```yaml
   - term: "Your Term"
     definition: "Clear, concise definition"
     tags: ["category1", "category2"]
     links:
       - title: "Related Resource"
         url: "https://example.com"
   ```
3. Commit your changes - the glossary will automatically update

*Last updated: `r Sys.Date()`*